Cloud correction and filtering of operational microwave humidity radiances with case specific uncertainty estimation

### 2020-09-23 Article/ici_submm_cloudcorr.tex
added first version of abstract

\begin{abstract}
TEXT
\end{abstract}

@@

In order to analyse the prediction uncertainty, the deviations of predicted quantiles from its median value are estimated. Fig.~\ref{fig:prediction_uncertainty_I2V} shows the spread of prediction uncertainties over different quantiles for randomly chosen 1500 cases. The large spread in the predicted errors indicates that QRNN is successful in representing uncertainties for each case individually, rather than expressing them as a single measure for all cases. In the latter case, the uncertainty estimates would be concentrated along a narrow interval. Among the cases associated with low uncertainty, the distribution is quite symmetric along the median value. These cases are concentrated along a narrow interval and lie close to the black curve. On the contrast, cases with high uncertainty are unequally spaced and have a larger spread over positive quantiles than negative quantiles.

Fig.~\ref{fig:predicted_errors} shows the comparison of observed errors (prediction accuracy) to predicted errors. The predicted dataset is constructed by drawing random samples from the posteriori distribution. We do not derive any sample from outside $\pm3\sigma$.  The predicted error is deviation of random sample to its median. For QRNN-single, the predicted and observed errors have good agreement for the peak of the distribution, but the predicted errors are spread out asymmetrically. For QRNN-all, the predicted and observed errors have a better agreement and the spread is symmetric for the former. The results show that both QRNN-single and QRNN-all are not able to represent the left wings of the distribution. This could also be a sampling issue, as the high errors we try to predict form a very small fraction of the complete dataset.

>>>>

\begin{abstract}

This study presents a cloud filtering and correction method for microwave humidity radiances. The method is based on the postulation that sub-millimeter(sub-mm) frequencies can provide a basis for cloud filtering/correction of data measured around 183\,GHz. A quantile regression(QRNN) based approach is formulated to estimate the posterior distributions of noise free clear sky (NFCS) radiances. QRNNs are trained to correct the cloud impact for each 183\,GHz channel using measurements from the target channel and available sub-mm channels. The approach is demonstrated by application to Ice Cloud Imager(ICI) and MicroWave Imager (MWI). As a special case applicability to smaller satellite missions like Arctic Weather Satellite (AWS), with fewer sub-mm channels, is also evaluated. The performance of QRNN based cloud filtering is also investigated. The results are compared against the NFCS simulations.

Pure-filtering approach is only partially successful in removing the cloud contamination. Though most of the cases with high cloud impact are drawn out, cases with low cloud impact are falsely classified as cloudy. This shortcoming is unacceptable in retrieval and assimilation applications and reinforces the necessity for cloud correction. The results from cloud correction show that QRNN is successful in alleviating the cloud contamination to a large extent. Few cases with residual cloud impact deteriorate the performance but filtering out such cases results in error distributions which are symmetric and have low bias and standard deviation. In some cases, the combination of 183\,GHz and sub-mm channels also results in a lower variability than noise. Another advantage of using QRNN is that predicted quantiles can be employed to quantify the case-specific uncertainty estimates.  The results show that QRNN is successful in representing the uncertainty for most of scenes individually. Despite individual variations for each channel, it is observed that uncertainty consistently increases with the error in the performance.

The results show that it can be highly recommended to use all available sub-mm frequencies to estimate the NFCS values of radiances/brightness temperatures. The strategy works well even when only one of the higher frequencies is available. This study uses simulated data, but we can expect to obtain similar performance when data fron the new sensors will be available.

\end{abstract}

@@

In order to analyse the prediction uncertainty, the deviations of predicted quantiles from its median value are estimated. Fig.~\ref{fig:prediction_uncertainty_I2V} shows the spread of prediction uncertainties over different quantiles for randomly chosen 1500 cases. The large spread in the predicted errors indicates that QRNN is successful in representing uncertainties for each case individually, rather than expressing them as a single measure for all cases. In the latter case, the uncertainty estimates would be concentrated along a narrow interval. Among the cases associated with low uncertainty, the distribution is quite symmetric along the median value. These cases are concentrated along a narrow interval and lie close to the black curve representing a Gaussian spread. On the contrast, cases with high uncertainty are unequally spaced and have a larger spread over positive quantiles than negative quantiles. Thus QRNN is capable of capturing non-Gaussian  error distributions as well.

Fig.~\ref{fig:predicted_errors} shows the comparison of observed errors (prediction accuracy) to predicted errors. The predicted dataset is constructed by drawing random samples from the posteriori distribution. We do not derive any sample from outside $\pm3\sigma$.  The predicted error is deviation of random sample to its median. For QRNN-single, the predicted and observed errors have good agreement for the peak of the distribution, but the predicted errors are spread out asymmetrically. For QRNN-all, the predicted and observed errors have a better agreement and the spread is symmetric for the former. The results show that both QRNN-single and QRNN-all are not able to represent the left wings of the distribution. This could also be a sampling issue, as the high errors we try to predict constitute a very small part of the complete dataset.
